Anonymous provision of services via blockchain

### 2022-12-02 paper/access.tex
update paper

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal
information~\cite{smith2011information}.

Such personal information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.

@@

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity} or did not address the conflict
between parties~\cite{altawy2017lelantos}.

@@

Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.

@@

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide
fair exchange guarantees.

@@

Themis~\cite{meng2019themis} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

@@

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers. The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers. As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.

@@

Themis~\cite{meng2019themis} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

@@

\subsection{Message Board}\label{sec:message-board}
The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

@@

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved}, trusted timestamping~\cite{gipp2015decentralized}, or message board~\cite{hinarejos2019solution}. In this work, we call it a message board.

@@

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.

@@

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the user's identity. Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeney2002k}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.

@@

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonyms. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}), ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), and Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsev2019tornado} (via zkSNARK~\cite{groth2016size} and MiMC~\cite{albrecht2016mimc}), Bitcoin's Wasabi\cite{WasabiWa56} (via CoinJoin \cite{CoinJoin41}).

@@

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

@@

In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction. As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API \cite{Howtopro46}. ZCash provides a mechanism called Payment Disclosure \cite{AnIntrod25}.

@@

One approach would be to post the result into a blockchain. However, storing data on a blockchain is very expensive. The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benet2014ipfs}. Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.

@@

\item Anonymous payments: Monero \cite{van2013cryptonote}, ZCash
  \cite{sasson2014zerocash}, Grin \cite{fuchsbauer2019aggregate},
  Tornado Cash \cite{pertsev2019tornado}.
\item Message board: Stampery \cite{de2016stampery}, Proof of Existence
  \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
  \cite{Chainpoi39} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benet2014ipfs}, Filecoin
  \cite{benetfilecoin} (runs on top of IPFS), or Ethereum's
  Swarm\cite{swarmwhi49}.
\end{enumerate}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS~\cite{Contenta59}. However, since our protocol does not depend on
this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{monero-blockchain}.
  \item{Storage netowork} — we use the Powergate, which is a wrapper around Filecoin and IPFS \cite{ipfs}.
  \item{Message board} — we use the Ethereum blockchain \cite{ethereum-blockchain}; concretely, Truffle Ganache and Solidity language.
  \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption. We use MetaMask browser extension for signing and submiting transactions to Ethereum's node. We use `monerod` and `monero-wallet-cli' command-line tools for interacting with Monero blockchain.
\end{itemize}

@@

Moreover, Powergate (storage network) is configured to use local Filecoin and IPFS networks.
For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
Monero is configured to use the public stage network.

@@

1. The protocol starts with the Customer opening the webapp and creating new provision. 
The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
The private key must be stored and provided later for the decryption of the results.

2. The Customer prints the QR code and put it on a package.

3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.

4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.

5. Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
 If the provision is paid with cash, the SP proceed to the step 8. Otherwise, the SP waits until the Customer pays for the provision.

6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.

7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .

8. The SP starts providing the service and outputs the file `result.pdf`.

9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.

10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.

11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
 Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'. Then the results are decrypted using previously stored client's private key.

@@

Justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{Web3Wiki71}.

The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (ii) make it infeasible to provide incorrect results.

@@

The second approach is more philosophical and visionary. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted. It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to represent blood digitally?''. If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured. Therefore, wrong service provision would be infeasible.

@@

Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS. The problem is that nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute. We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{benetfilecoin}. With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction. Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.

@@

We assumed the customer to deliver the package to the SP personally or via a trusted person. However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}. One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology. 
Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{js access.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
He is currently with the Department of Computer
Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology. He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
His research results find applications in web search engines and systems of automated text categorization. He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language. Besides his research in information retrieval domain, he was involved in projects related to cognitive science. His mainstream of this research is building semantic memory models that improve natural language processing. He also worked on analyzing
human emotions, by mining EEG signals. His results are implemented in
the form of brain-machine interfaces for disabled people. He also works
on analyzing data within the IoT domain and its secure storage on the blockchain. 
He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.

@@

  \item
    \(\operatorname{\sigma_{3, c, \n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
  \item
    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

@@

Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.

@@

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a
fair exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide
fair exchange guarantees.

@@

Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

@@

Lelanros~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
physical delivery system. The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers. The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers. As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.

@@

Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

@@

\subsection{Message Board}\label{sec:message-board}
The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{ProofExistenceOnline, crespoStamperyBlockchainTimestamping2017, ChainpointBlockchainProof}.

@@

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}. In this work, we call it a message board.

@@

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}. For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.

@@

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the user's identity. Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.

@@

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonyms. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{moneroBulletproofsMoneropediaMonero, bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{https://wasabiwallet.io/} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).

@@

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

@@

In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction. As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API \cite{MoneroHowProve}. ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.

@@

One approach would be to post the result into a blockchain. However, storing data on a blockchain is very expensive. The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}. Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.

@@

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
  \cite{protocollabsFilecoinDecentralizedStorage2017} (runs on top of IPFS), or Ethereum's
  Swarm\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{https://docs.ipfs.tech/concepts/content-addressing}. However, since our protocol does not depend on
this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
  \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption. We use MetaMask browser extension for signing and submiting transactions to Ethereum's node. We use `monerod` and `monero-wallet-cli' command-line tools for interacting with Monero blockchain.
\end{itemize}

@@

Moreover, Powergate is configured to use local Filecoin and IPFS networks.
For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
Monero is configured to use the public stage network.

@@

\begin{itemize}
  \item 1. The protocol starts with the Customer opening the webapp and creating new provision. 
The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
The private key must be stored and provided later for the decryption of the results.

  \item 2. The Customer prints the QR code and put it on a package.

  \item 3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.

  \item 4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.

  \item 5. Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
 If the provision is paid with cash, the SP proceed to the step 8. Otherwise, the SP waits until the Customer pays for the provision.

  \item 6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.

  \item 7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .

  \item 8. The SP starts providing the service and outputs the file `result.pdf`.

  \item 9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.

  \item 10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.

  \item 11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
 Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'. Then the results are decrypted using previously stored client's private key.

@@

Justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.

The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019} or Kleros~\cite{bergollaKlerosSociolegalCase2022}; or (ii) make it infeasible to provide incorrect results.

@@

The second approach is more philosophical and visionary. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted. It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to represent blood digitally?''. If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured. Therefore, wrong service provision would be infeasible.

@@

Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS. The problem is that nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute. We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017}. With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction. Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.

@@

We assumed the customer to deliver the package to the SP personally or via a trusted person. However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017}. One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology. 
Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julina.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
He is currently with the Department of Computer
Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology. He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
His research results find applications in web search engines and systems of automated text categorization. He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language. Besides his research in information retrieval domain, he was involved in projects related to cognitive science. His mainstream of this research is building semantic memory models that improve natural language processing. He also worked on analyzing
human emotions, by mining EEG signals. His results are implemented in
the form of brain-machine interfaces for disabled people. He also works
on analyzing data within the IoT domain and its secure storage on the blockchain. 
He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.

@@

  \item
    \(\operatorname{\sigma_{3, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
  \item
    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:
